---
title: "AS3-2: 股市動態"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

[第四組] `M074020010 陳韻卉` `M074020036 張哲瑋` `M074020043 巢正修` `B046060005陳雅靜` `B046060016 戴婉錡` `B046060037	陳柏愷`

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 
```{r}
IBM = read.csv("data/IBMStock.csv", stringsAsFactors=F)
GE  = read.csv("data/GEStock.csv", stringsAsFactors=F)
ProcterGamble = read.csv("data/ProcterGambleStock.csv", stringsAsFactors=F)
CocaCola = read.csv("data/CocaColaStock.csv", stringsAsFactors=F)
Boeing = read.csv("data/BoeingStock.csv", stringsAsFactors=F)
Sys.setlocale('LC_ALL','C') #更改R預設語系
```

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價
```{r}
IBM
GE
ProcterGamble
CocaCola
Boeing
```

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
#用nrow顯示資料有幾列
nrow(IBM) 
nrow(GE)
nrow(ProcterGamble)
nrow(CocaCola)
nrow(Boeing)
#ANS:480
```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
#整理時間格式
IBM$Date = as.Date(IBM$Date, format = "%m/%d/%y")
GE$Date = as.Date(GE$Date, format = "%m/%d/%y")
ProcterGamble$Date = as.Date(ProcterGamble$Date, format = "%m/%d/%y")
CocaCola$Date =  as.Date(CocaCola$Date, format = "%m/%d/%y")
Boeing$Date =  as.Date(Boeing$Date, format = "%m/%d/%y")

#查看每個資料框的最早時間(在已知資料按時間排序的情況下)
IBM$Date[1]
GE$Date[1]
ProcterGamble$Date[1]
CocaCola$Date[1]
Boeing$Date[1]

#ANS:1970
```

__§ 1.3__ What is the latest year in our datasets?
```{r}
#查看每個資料框的最晚時間(在已知資料按時間排序的情況下)
IBM$Date[480]
GE$Date[480]
ProcterGamble$Date[480]
CocaCola$Date[480]
Boeing$Date[480]

#ANS:2009
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
#計算IBM1997年到2009年的平均股價
mean(IBM$StockPrice)

#ANS:144.4
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
#計算GE1997年到2009年的最低股價
min(GE$StockPrice)

#ANS:9.294
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
#計算CocaCola1997年到2009年的最高股價
max(CocaCola$StockPrice)

#ANS:146.6
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
#計算Boeing1997年到2009年的股價中位數
median(Boeing$StockPrice)

#ANS:44.88
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
#計算P&G1997年到2009年的股價標準差
sd(ProcterGamble$StockPrice)

#ANS:18.19
```

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period? 

```{r}
#找出CocaCola股價最高及最低的日期
CocaCola$Date[which.max(CocaCola$StockPrice)]
#1973/01/01最高
CocaCola$Date[which.min(CocaCola$StockPrice)]
#1980/03/01最低
#ANS:擁有最高股價年分:1973 / 擁有最低股價年分:1980
```


__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
#以plot繪製CocaCola折線圖
plot(CocaCola$Date, CocaCola$StockPrice,  xlab="Year", ylab="Stock price", type="l", col="Blue")
#用lines加入P&G共同比較
lines(ProcterGamble$Date, ProcterGamble$StockPrice, col="Red")
#加入直線標示時間點
abline(v=as.Date(c("2000-03-01")), lwd=1)

#ANS:ProcterGamble dropped more 
```

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
#以plot繪製CocaCola折線圖
plot(CocaCola$Date, CocaCola$StockPrice, xlab = "Year", ylab = "Stock price", type = "l", col = "Blue")
#用lines加入P&G共同比較
lines(ProcterGamble$Date, ProcterGamble$StockPrice, col="Red")
#加入直線標示時間點
abline(v=as.Date(c("1983-01-01")), lwd=2)

#也可直接透過數值計算
CocaCola$Date[168]
CocaCola$Date[157]
ProcterGamble$Date[168]
ProcterGamble$Date[157]
CocaCola$StockPrice[168]-CocaCola$StockPrice[157]
ProcterGamble$StockPrice[168]-ProcterGamble$StockPrice[157]

#ANS:Going up:CocaCola / Going down:ProcterGamble
```

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
#
#

#根據上兩題的折線圖所示，P&G明顯高於CocaCola
#運用平均數證實
mean(ProcterGamble$StockPrice)>mean(CocaCola$StockPrice)


#ANS:P&G
```


<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
#以plot繪製IBM折線圖
plot(IBM$Date, IBM$StockPrice, xlab="Year", ylab="Stock price", type="l", col="Red")
#用lines加入其他幾支股票共同比較
lines(GE$Date, GE$StockPrice, col="Orange")
lines(CocaCola$Date, CocaCola$StockPrice, col="Blue")
lines(ProcterGamble$Date, ProcterGamble$StockPrice, col="Green")
lines(Boeing$Date, Boeing$StockPrice, col="Yellow")
#用abline標示時間點
abline(v=as.Date(c("2000-03-01")), lwd=1)

#ANS:GE
```

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
#依據3.1的折線圖所示，紅線達到最高值
#ANS:IBM
```

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
#以plot繪製IBM折線圖
#1997/09/01為第333個觀察值，1997/11/01為第335個觀察值
plot(IBM$Date[333:335], IBM$StockPrice[333:335], xlab="Year", ylab="Stock price", type="l", col="Red", ylim = c(0,200))
#用lines加入其他幾支股票共同比較
lines(GE$Date[333:335], GE$StockPrice[333:335], col="Orange")
lines(CocaCola$Date[333:335], CocaCola$StockPrice[333:335], col="Blue")
lines(ProcterGamble$Date[333:335], ProcterGamble$StockPrice[333:335], col="Green")
lines(Boeing$Date[333:335], Boeing$StockPrice[333:335], col="Yellow")
#或是用減法
Boeing$StockPrice[335]>Boeing$StockPrice[333]
CocaCola$StockPrice[335]>CocaCola$StockPrice[333]
GE$StockPrice[335]>GE$StockPrice[333]
IBM$StockPrice[335]>IBM$StockPrice[333]
ProcterGamble$StockPrice[335]>ProcterGamble$StockPrice[333]
#ANS:P&G, Boeing
```

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
#以plot繪製IBM折線圖
#2004/01/01為第409個觀察值，2005/12/01為第432個觀察值
plot(IBM$Date[409:432], IBM$StockPrice[409:432], xlab="Year", ylab="Stock price", type="l", col="Red", ylim = c(0,200))
#用lines加入其他幾支股票共同比較
lines(GE$Date[409:432], GE$StockPrice[409:432], col="Orange")
lines(CocaCola$Date[409:432], CocaCola$StockPrice[409:432], col="Blue")
lines(ProcterGamble$Date[409:432], ProcterGamble$StockPrice[409:432], col="Green")
lines(Boeing$Date[409:432], Boeing$StockPrice[409:432], col="Yellow")
#或是用減法
IBM$StockPrice[432]-IBM$StockPrice[409]
GE$StockPrice[432]-GE$StockPrice[409]
CocaCola$StockPrice[432]-CocaCola$StockPrice[409]
ProcterGamble$StockPrice[432]-ProcterGamble$StockPrice[409]
Boeing$StockPrice[432]-Boeing$StockPrice[409]
#ANS:Boeing
```


<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
#比較IBM單月平均股價與總平均股價，哪個比較高
tapply(IBM$StockPrice,months(IBM$Date),mean) %>%sort(decreasing = TRUE)>mean(IBM$StockPrice)
tapply(IBM$StockPrice,months(IBM$Date),mean) %>%sort(decreasing = TRUE)
#February,March,April,May,January的平均股價皆大於總平均股價，而February的平均股價是12個月裡最高的
```

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
#
tapply(GE$StockPrice,months(GE$Date),mean) %>%sort(decreasing = TRUE)
tapply(CocaCola$StockPrice,months(CocaCola$Date),mean) %>%sort(decreasing = TRUE)
#從表上顯示，四月皆為他們平均股價最高的月份
```

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
#每個公司的股價在1月及12月哪個月份的股價較低
plot(tapply(Boeing$StockPrice, months(Boeing$Date), mean),xlab = "month",ylab = "stock price")
plot(tapply(CocaCola$StockPrice, months(CocaCola$Date), mean),xlab = "month",ylab = "stock price")
plot(tapply(GE$StockPrice, months(GE$Date), mean),xlab = "month",ylab = "stock price")
plot(tapply(IBM$StockPrice, months(IBM$Date), mean),xlab = "month",ylab = "stock price")
plot(tapply(ProcterGamble$StockPrice, months(ProcterGamble$Date), mean),xlab = "month",ylab = "stock price")
#12月的股價皆較1月低。
```

<br><br><br>

