---
title: "AS3-3: 美國的人口統計和就業資料"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

[第四組] `M074020010 陳韻卉` `M074020036 張哲瑋` `M074020043 巢正修` `B046060005陳雅靜` `B046060016 戴婉錡` `B046060037	陳柏愷`

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)

Sys.setlocale("LC_ALL", "English")

```
<hr>

就業統計數據是政策制定者用來衡量經濟整體實力的最重要指標之一。在美國，政府使用現有人口調查（CPS）衡量失業率，該調查每月收集來自各種美國人的人口統計和就業信息。在本練習中，我們將使用講座中審查的主題以及一些使用2013年9月版的，具有全國代表性的數據集。數據集中的觀察結果代表2013年9月CPS中實際完成調查的人員，完整數據集有385個欄位，但在本練習中，我們將使用數據集CPSData.csv版本，它具有以下欄位：

+ `PeopleInHousehold`: 受訪者家庭中的人數。
+ `Region`: 受訪者居住的人口普查區域。
+ `State`: 受訪者居住的州。
+ `MetroAreaCode`: 都會區代碼，如受訪者不住都會區，則為NA；從代碼到都會區名稱的對應在`MetroAreaCodes.csv`中提供。
+ `Age`: 受訪者的年齡，以年為單位。 80代表80-84歲的人，85代表85歲及以上的人。
+ `Married`: 受訪者的婚姻狀況。
+ `Sex`: 受訪者的性別。
+ `Education`: 受訪者獲得的最高教育程度。
+ `Race`: 受訪者的種族。
+ `Hispanic`: 受訪者是否屬於西班牙裔。
+ `CountryOfBirthcode`: 識別受訪者出生國家的代碼。從代碼到國家名稱的映射在CountryCodes.csv文件中提供。
+ `Citizenship`: 受訪者的公民身份。
+ `EmploymentStatus`: 受訪者的就業狀況。
+ `Industry`: 受訪者的就業行業（僅在受僱的情況下可用）。

- - -

<br><br>

###  Section-1 Loading and Summarizing the Dataset

__§ 1.1__ How many interviewees are in the dataset?
```{r}
CPS = read.csv("data/CPSData.csv")
nrow(D)
```

__§ 1.2__ Among the interviewees with a value reported for the Industry variable, what is the most common industry of employment? Please enter the name exactly how you see it.
```{r}
table(CPS$Industry) %>% sort(decreasing = T) %>% head
#從事Educational and health services相關者人數最多
```

__§ 1.3__ Which state has the fewest interviewees?
```{r}
table(CPS$State) %>% sort(decreasing = F) %>% head
#New Mexico是最少受訪者的州
```

Which state has the largest number of interviewees?
```{r}
table(CPS$State) %>% sort(decreasing = T) %>% head
#California是最多受訪者的州
```


__§ 1.4__ What proportion of interviewees are citizens of the United States?


```{r}
levels(CPS$Citizenship)
#欄位Citizenship有三種level:  "Citizen, Native" , "Citizen, Naturalized" , "Non-Citizen" 

nrow(subset(CPS,Citizenship != "Non-Citizen"))/nrow(CPS)
# 非Non-Citizen人數/全部人數
```

__§ 1.5__ For which races are there at least 250 interviewees in the CPS dataset of Hispanic ethnicity? (Select all that apply.) 

+ American Indian (O)
+ Asian 
+ cBlack (O)
+ Multiracial (O)
+ Pacific Islander
+ White (O)

```{r}
#Hispanic ethnicity 西班牙裔
table(CPS[CPS$Hispanic == 1,"Race"]) > 250
```


<br><br> 

- - -

###  Section-2 Evaluating Missing Values

__§ 2.1__ Which variables have at least one interviewee with a missing (NA) value? (Select all that apply.)

+ PeopleInHousehold
+ Region
+ State
+ MetroAreaCode (O)
+ Age
+ Married (O)
+ Sex
+ Education (O)
+ Race
+ Hispanic
+ CountryOfBirthCode
+ Citizenship
+ EmploymentStatus (O)
+ Industry (O)

```{r}
sapply(colnames(CPS),function(x) mean(is.na(CPS[,x])))
#is.na會返回boolean值(資料點是否為NA，是返回True)，以mean計算來代表這個欄位有多少比例為NA
```

__§ 2.2__  Which is the most accurate:

+ The Married variable being missing is related to the Region value for the interviewee.
+ The Married variable being missing is related to the Sex value for the interviewee.
+ (O) The Married variable being missing is related to the Age value for the interviewee. 
+ The Married variable being missing is related to the Citizenship value for the interviewee.
+ The Married variable being missing is not related to the Region, Sex, Age, or Citizenship value for the interviewee.

```{r}
plot(factor(is.na(CPS$Married)),CPS$Age)
#可以看到20歲以下的人幾乎Married欄位都是NA，20歲以上Married都有值
```


__§ 2.3__ How many states had all interviewees living in a non-metropolitan area (aka they have a missing MetroAreaCode value)? For this question, treat the District of Columbia as a state (even though it is not technically a state).
```{r}
A = table(CPS$State,is.na(CPS$MetroAreaCode)) %>% as.data.frame()
#將State,is.na(D$MetroAreaCode的列連表存入一個dataframe)
A[A$Var2 == "FALSE" & A$Freq == 0,"Var1"]
#篩選is.na的FALSE數量為0的State (所有MetroAreaCode都是NA)
#ans:Alaska,Wyoming
``` 


How many states had all interviewees living in a metropolitan area? Again, treat the District of Columbia as a state.
```{r}
A[A$Var2 == "TRUE" & A$Freq == 0,"Var1"] #所有MetroAreaCode都不是NA
#ans: District of Columbia New Jersey , Rhode Island
```

__§ 2.4__ Which region of the United States has the largest proportion of interviewees living in a non-metropolitan area?
```{r}
table(CPS$Region,is.na(CPS$MetroAreaCode)) 
# Midwest 有最大的non-metropolitan比例 100674/(20010+10674)

```

__§ 2.5__ Which state has a proportion of interviewees living in a non-metropolitan area closest to 30%?

`tapply` : tapply(X,INDEX,FUN)  X是一組向量，INDEX是一組和X有相同長度的factor類型向量。將X根據INDEX的值進行分組，每組丟入funtion
```{r}
sort(tapply(is.na(CPS$MetroAreaCode),CPS$State,mean))
#State是factor，將is.na(D$MetroAreaCode)根據每個不同的State來分組計算平均，得到每個Statek的non-metropolitan比例。

#ans: Wisconsin 0.29932986
```

Which state has the largest proportion of non-metropolitan interviewees, ignoring states where all interviewees were non-metropolitan?
```{r}
#如上表
#ans: Montana
```

<br><br> 

- - -

###  Section-3 Integrating Metropolitan Area Data

Codes like MetroAreaCode and CountryOfBirthCode are a compact way to encode factor variables with text as their possible values, and they are therefore quite common in survey datasets. In fact, all but one of the variables in this dataset were actually stored by a numeric code in the original CPS datafile.

When analyzing a variable stored by a numeric code, we will often want to convert it into the values the codes represent. To do this, we will use a dictionary, which maps the the code to the actual value of the variable. We have provided dictionaries MetroAreaCodes.csv and CountryCodes.csv, which respectively map MetroAreaCode and CountryOfBirthCode into their true values. Read these two dictionaries into data frames MetroAreaMap and CountryMap.


__§ 3.1__ How many observations (codes for metropolitan areas) are there in MetroAreaMap?
```{r}
M = read.csv("data/MetroAreaCodes.csv")
C = read.csv("data/CountryCodes.csv")
```

How many observations (codes for countries) are there in CountryMap?
```{r}
nrow(M)
```

__§ 3.2__ What is the name of the variable that was added to the data frame by the merge() operation?

To merge in the metropolitan areas, we want to connect the field MetroAreaCode from the CPS data frame with the field Code in MetroAreaMap. The following command merges the two data frames on these columns, overwriting the CPS data frame with the result:

```{r}
CPS = merge(CPS,M, by.x="MetroAreaCode", by.y="Code", all.x=TRUE)
#根據C的MetroAreaCode欄位和M的Code欄位 合併在一起，all.x代表即使C中有資料的MetroAreaCode不存在於M的Code，也要將資料留下來，對不到的M資料部份以NA填值
```

How many interviewees have a missing value for the new metropolitan area variable?
```{r}
sum(is.na(CPS$MetroArea))
```

__§ 3.3__ Which of the following metropolitan areas has the largest number of interviewees?

+ Atlanta-Sandy Springs-Marietta, GA
+ Baltimore-Towson, MD
+ Boston-Cambridge-Quincy, MA-NH (O)  - which has 2229 interviewees
+ San Francisco-Oakland-Fremont, CA

```{r}
table(CPS$MetroArea) %>% sort(decreasing = T) %>% head(10)
```

__§ 3.4__ Which metropolitan area has the highest proportion of interviewees of Hispanic ethnicity?
```{r}
tapply(CPS$Hispanic,CPS$MetroArea,mean) %>% sort(decreasing = T) %>% head
#Laredo, TX有最高比例的Hispanic ethnicity人數
```

__§ 3.5__ Determine the number of metropolitan areas in the United States from which at least 20% of interviewees are Asian.
```{r}
levels(CPS$Race) #Race: Asian
tapply(CPS$Race == "Asian",CPS$MetroArea,mean) %>% sort(decreasing = T) %>% head
#4個metropolitan areas有至少20%的亞洲人
```

__§ 3.6__  Passing na.rm=TRUE to the tapply function, determine which metropolitan area has the smallest proportion of interviewees who have received no high school diploma.
```{r}
levels(CPS$Education) #Education: No high school diploma
tapply(CPS$Education == "No high school diploma",CPS$MetroArea,mean,na.rm = T) %>% sort(decreasing = F) %>% head

#ans: Iowa City, IA 有最少比例的人教育程度是no high school diploma
```


<br><br> 

- - -

###  Section-4 Integrating Country of Birth Data

Just as we did with the metropolitan area information, merge in the country of birth information from the CountryMap data frame, replacing the CPS data frame with the result. If you accidentally overwrite CPS with the wrong values, remember that you can restore it by re-loading the data frame from CPSData.csv and then merging in the metropolitan area information using the command provided in the previous subproblem.

```{r}
CPS = merge(CPS,C,by.x = "CountryOfBirthCode",by.y = "Code" , all.x = T)
```

__§ 4.1__ What is the name of the variable added to the CPS data frame by this merge operation?
```{r}
#新增了Country欄位
```

How many interviewees have a missing value for the new country of birth variable?
```{r}
sum(is.na(CPS$Country))
```

__§ 4.2__ Among all interviewees born outside of North America, which country was the most common place of birth?
```{r}
#在北美以外的人最多在哪個country出生
levels(CPS$Region)
table(CPS$Country[CPS$Region != "Northeast"]) %>% sort(decreasing = T) %>% head

#ans: Philippines
#前兩名United States和Mexico都是在北美洲，答案為第三名Philippines
```

__§ 4.3__ What proportion of the interviewees from the "New York-Northern New Jersey-Long Island, NY-NJ-PA" metropolitan area have a country of birth that is not the United States?
For this computation, don't include people from this metropolitan area who have a missing country of birth

```{r}
#來自New York-Northern New Jersey-Long Island, NY-NJ-PA的人有多少比例不是出生在美國？

mean(CPS$Country[which(CPS$MetroArea == "New York-Northern New Jersey-Long Island, NY-NJ-PA")] != "United States",na.rm = T)

#na.rm代表不計算CPS$Country為NA的資料，不去掉的話計算mean會是NA
```

__§ 4.4__ Which metropolitan area has the largest number (note -- not proportion) of interviewees with a country of birth in India? 
```{r}
tapply(CPS$Country == "India",CPS$MetroArea,sum) %>% sort(decreasing = T) %>% head
#ans: Detroit-Warren-Livonia, MI
```

In Brazil?
```{r}
tapply(CPS$Country == "Brazil",CPS$MetroArea,sum) %>% sort(decreasing = T) %>% head
#ans: Boston-Cambridge-Quincy, MA-NH
```

In Somalia?
```{r}
tapply(CPS$Country == "Somalia",CPS$MetroArea,sum) %>% sort(decreasing = T) %>% head
#ans: Phoenix-Mesa-Scottsdale, AZ
```

<br><br><br>
