---
title: "AS3-1: 數位偵探"
author: "第 4 組"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

[第四組] `M074020010 陳韻卉` `M074020036 張哲瑋` `M074020043 巢正修` `B046060005陳雅靜` `B046060016 戴婉錡` `B046060037	陳柏愷`


```{r results='hide', message=FALSE, warning=FALSE, echo=F}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr, d3heatmap)
```
<hr>

犯罪是一個國際關注的問題，但它在不同的國家以不同的方式記錄和處理。 在美國，聯邦調查局（FBI）記錄了暴力犯罪和財產犯罪。 此外，每個城市都記錄了犯罪行為，一些城市發布了有關犯罪率的數據。 伊利諾伊州芝加哥市從2001年開始在線發布犯罪數據。

芝加哥是美國人口第三多的城市，人口超過270萬。在這個作業裡面，我們將關注一種特定類型的財產犯罪，稱為「汽車盜竊」，我們將使用R中的一些基本數據分析來了解芝加哥的汽車盜竊紀錄。請載入文件"data/mvtWeek1.csv"：以下是各欄位的描述：

+ `ID`: a unique identifier for each observation
+ `Date`: the date the crime occurred
+ `LocationDescription`: the location where the crime occurred
+ `Arrest`: whether or not an arrest was made for the crime (TRUE if an arrest was made, and FALSE if an arrest was not made)
+ `Domestic`: whether or not the crime was a domestic crime, meaning that it was committed against a family member (TRUE if it was domestic, and FALSE if it was not domestic)
+ `Beat`: the area, or "beat" in which the crime occurred. This is the smallest regional division defined by the Chicago police department.
+ `District`: the police district in which the crime occured. Each district is composed of many beats, and are defined by the Chicago Police Department.
+ `CommunityArea`: the community area in which the crime occurred. Since the 1920s, Chicago has been divided into what are called "community areas", of which there are now 77. The community areas were devised in an attempt to create socially homogeneous regions.
+ `Year`: the year in which the crime occurred.
+ `Latitude`: the latitude of the location at which the crime occurred.
+ `Longitude`: the longitude of the location at which the crime occurred.

<br>

- - -

###  Section-1 Loading the Data

【1.1】How many rows of data (observations) are in this dataset?
```{r}
A = read.csv("data/mvtWeek1.csv" , stringsAsFactors = FALSE)
nrow(A)
#先讀取資料並取名為A，並列出Ａ資料共有幾筆。
```


```{r}
summary(A)
#檢查各欄位的資料格式
```

類別(Factor) versus 字串(Character)

【1.2】How many variables are in this dataset?
```{r}
ncol(A)
#總共有11個欄位
```


【1.3】Using the "max" function, what is the maximum value of the variable "ID"?
```{r}
max(A$ID)
#ID欄位的最大值
```


【1.4】 What is the minimum value of the variable "Beat"?
```{r}
min(A$Beat)
#Beat欄位的最小值
```


【1.5】 How many observations have value TRUE in the Arrest variable (this is the number of crimes for which an arrest was made)?
```{r}
sum(A$Arrest , na.rm = FALSE)
#總共有逮捕到的案件總數，空值忽略
```

【1.6】 How many observations have a LocationDescription value of ALLEY?
```{r}
sum(A$LocationDescription == "ALLEY")
#案件發生地點是在巷弄(Alley)中的總數
```


<br><br>

- - -

### Section-2 Understanding Dates in R

【2.1】 In what format are the entries in the variable Date?

+ Month/Day/Year Hour:Minute
+ Day/Month/Year Hour:Minute
+ Hour:Minute Month/Day/Year
+ Hour:Minute Day/Month/Year

```{r}
head(A$Date )
#顯示出前幾項Date的資料內容
```

```{r}
ts = as.POSIXct(A$Date, format = "%m/%d/%y %H:%M")
par(cex = 0.7)
hist(ts, "year", las = 2,freq = T,xlab = "")
#先將Date的資料從"字串"轉為"時間"再畫成長條圖，x軸以年份為區分，las將橫的字轉為直的，以增加易讀性。y軸以頻率為區分。
```

```{r}
table(format(ts,'%w'))
#計算出案件發生在星期一到星期日的個別次數
```

```{r fig.height=2.5, fig.width=8}
table(format(ts, '%m'))
#計算出案件發生在1月到12月的個別次數

table(weekdays = format(ts,'%w'), month = format(ts,'%m'))
#計算出歷年每月各星期的案件發生次數
```

```{r}
table(format(ts, "%u"), format(ts, "%H")) %>%
  as.data.frame.matrix %>%
  d3heatmap(F,F,col=colorRamp(c('seagreen','lightyellow','red')))
#以周跟小時來畫出偷竊率的熱點圖，依程度分低到高，綠色表低、黃色表中、紅色表高。(heatmap必須以matrix形式才可接受資料)
```


【2.2】 What is the month and year of the median date in our dataset? 
```{r}
median(ts)
#資料ts中最中間的資料
```

【2.3】 In which month did the fewest motor vehicle thefts occur?
```{r}
sort(table(format(ts, "%m")))
#歷年各月份案件發生總數，並將其排序(預設由小到大)
format(ts, "%m") %>%
  table %>%
  sort()
```

【2.4】 On which weekday did the most motor vehicle thefts occur?
```{r}
sort(table(format(ts, "%w")))
#歷年各星期案件發生總數，並將其排序(預設由小到大)
format(ts, "%w") %>%
  table %>%
  sort()
```

【2.5】 Which month has the largest number of motor vehicle thefts for which an arrest was made?
```{r}
ts[A$Arrest] %>%
  format('%m') %>%
  table %>%
  sort()
#歷年各月份Arrest到的案件個數，並進行排序
sort(table(format(ts[A$Arrest], "%m")))
```

<br><br>

- - -

### Section-3 Visualizing Crime Trends

【3.1】 (a) In general, does it look like crime increases or decreases from 2002 - 2012? (b) In general, does it look like crime increases or decreases from 2005 - 2008? (c) In general, does it look like crime increases or decreases from 2009 - 2011?
```{r}
hist(ts, 'year',las=2)
#(a)2002~2012 -> Decrease
#(b)2005~2008 -> Decrease
#(c)2009~2011 -> Increase
```

【3.2】 Does it look like there were more crimes for which arrests were made in the first half of the time period or the second half of the time period?
```{r}
table(ts > as.POSIXct("2007-01-01"))
#將時間分為上下兩半，小於2007年的資料為False，大於則為TRUE。

```

【3.3】 For what proportion of motor vehicle thefts in 2001 was an arrest made?
```{r}
table(A$Arrest, format(ts, '%Y')) %>%
  prop.table(2) %>%
  round(3)
#計算出歷年的案件破案率(prop.table(2)是指以col為單位去計算比率，round是計算到小數點後第三位)
```

【3.4】 For what proportion of motor vehicle thefts in 2007 was an arrest made?
```{r}
tapply(A$Arrest, format(ts, '%Y'), mean) %>%
  round(3) 
#以年份為主，去計算逮捕率的平均值。
#2007年為0.085
```

【3.5】 For what proportion of motor vehicle thefts in 2012 was an arrest made?
```{r}
tapply(A$Arrest, format(ts, '%Y'), mean) %>%
  round(3) 
#2012年為0.039
```

<br><br>

- - -

### Section-4 Popular Locations

【4.1】 Which locations are the top five locations for motor vehicle thefts, excluding the "Other" category? You should select 5 of the following options.

```{r}
table(A$LocationDescription) %>%
  sort %>%
  tail(6)
#計算出TOP 5 案件發生地點(因other之數量介於top5之中，所以必須多找一個數值出來)
```

【4.2】 How many observations are in Top5?
```{r}
(top5 = names(table(A$LocationDescription) %>%
                sort %>%
                tail(6))[-4])
#顯示出TOP5發生地點的名稱。([-4]是為了去除OTHER之地點)
```

【4.3】 One of the locations has a much higher arrest rate than the other locations. Which is it? 
```{r}
top5 = subset(A, LocationDescription %in% top5)
tapply(top5$Arrest, top5$LocationDescription, mean) %>%
  sort()
#先將TOP5發生地點的名稱之相對資料存入top5，再算出該地區的Arrest平均值。
```

【4.4】 On which day of the week do the most motor vehicle thefts at gas stations happen?
```{r}
ts[A$Location == "GAS STATION"] %>%
  format('%w') %>%
  table %>%
  sort()
#星期六發生的案件數為最多(地點為GAS STATION)
```

【4.5】 On which day of the week do the fewest motor vehicle thefts in residential driveways happen?
```{r}
ts[A$Location == "DRIVEWAY - RESIDENTIAL"] %>%
  format('%w') %>%
  table %>%
  sort()
#星期六發生的案件數為最少(地點為DRIVEWAY - RESIDENTIAL)
```


<br><br><br>


